### 2012-02-12 exam3/1.tex
First draft of problem 2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{ct} % tight CM font for \tt
\newexercise{exercise}{Exercise}[subsection]

@@

Here are data, class, and interface definitions for Shapes:
\begin{verbatim}
;; A Shape is one of:
;; - (rect% Number Number)
;; - (circ% Number)
;; implements:
;; bba : -> Number     (short for "bounding-box-area")
;; Compute the area of the smallest bounding box for this shape.

(define-class rect%
  (fields width height))

(define-class circ%
  (fields radius))
\end{verbatim}
%
Here are some examples of how \code{bounding-box-area} should work:
\begin{verbatim}
(check-expect ((rect% 3 4) . bba) 12)
(check-expect ((circ% 1.5) . bba)  9)
\end{verbatim}

\begin{enumerate}
\item Design the \code{bba} method for the
  \code{rect\%} and \code{circ\%} class.

\item Design a super class of \code{rect\%} and \code{circ\%} and
  lift the \code{bba} method to the super class.  Extend
  the shape interface as needed, but implement any methods you add.

\item Design a new variant of a Shape, Square, which should support
  all of the methods of the interface.
\end{enumerate}

\begin{solution}
\begin{verbatim}
;; Part 1 [6pt]
(define-class rect% 
  (fields width height)                
  (define/public (bba)                 [2pt]
    (* (field width) (field height))))

(define-class circ% 
  (fields radius)                      
  (define/public (bba)                 [2pt]
    (sqr (* 2 (field radius)))))

;; Part 2 [10pt]

;; implements:
;; width : -> Number                         [1pt]
;; height : -> Number
;; Compute the {width,height} of this shape. [1pt]

(define-class shape% 
  (define/public (bounding-box-area)
    (* (this . width) (this . height))))     [3pt]

(define-class rect% 
  (super shape%)                             [1pt]
  (fields width height))                     [1pt]

(define-class circ% 
  (super shape%)                             [1pt]
  (fields radius)
  (define/public (width)                     [1pt]
    (* 2 (field radius)))
  (define/public (height)                    [1pt]
    (width)))

;; Part 3 [4pt]

(define-class square%
  (super shape%)                             [1pt]
  (fields width)                             [1pt]
  (define/public (height)                    [1pt]
    (width)))

(check-expect ((square% 5) . bba) 25)        [1pt]
\end{verbatim}
\end{solution}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\usepackage{./exam}
\usepackage{type1cm} % We are using scalable fonts. Really.
\usepackage{alltt,times,comment,amsmath}
\usepackage{alltt}
\usepackage{ct} % tight CM font for \tt
\newexercise{exercise}{Exercise}[subsection]

@@

Here are data, class, and interface definitions for a list of numbers:
\begin{alltt}
;; An LoN is one of:
;; - (new mt%)
;; - (new cons% Number LoN)
;; and implements:
;; - sum : -> Number
;;   Compute the sum of the numbers in this list.
;; - sqrs : -> LoN
;;   List of squares of each number in this list.

(define-class mt%
  (define (sum) 0)
  (define (sqrs) this))

(define-class cons%
  (fields first rest)
  (define (sum)
    (+ (this . first)
       (this . rest . sum)))
  (define (sqrs)
    (new cons% 
         (sqr (this . first)) ; (sqr x) = x\(\sp{2}\)
         (this . rest . sqrs))))
\end{alltt}
%
Here are some examples:
\begin{verbatim}
(check-expect ((new mt%) . sum) 0)
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sum)  9)
(check-expect ((new mt%) . sqrs) (new mt%))
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sqrs)
              (new cons% 16 (new cons% 25 (new mt%))))
\end{verbatim}

\newpage
\noindent
Develop the \verb|sum-sqrs| method that computes the sum of the
squares of a list of numbers.  Here is an example:
\begin{verbatim}
(check-expect ((new cons% 4 (new cons% 5 (new mt%))) . sum-sqrs) 
              (+ 16 25))
\end{verbatim}

If you can, define a super class of \verb|mt%| and \verb|cons%| and
lift the definition of \verb|sum-sqrs| to this class.  (We will assume
the appropriate \verb|super| declaration in \verb|mt%| and
\verb|cons%|.)  If you cannot, define methods in both \verb|mt%| and
\verb|cons%| for partial credit.

\begin{solution}
\begin{verbatim}
(define-class list%
  (define (sum-sqrs)
    ((this . sqrs) . sum)))

(check-expect ((new mt%) . sum-sqrs) 0)
\end{verbatim}
\end{solution}

\newpage
\ifrubric\else
[Here is some more space for the previous problem.]
\newpage
\fi
